Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-28 nge.tex
Update rp on titan architecture

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{figures/architecture_compact_rp_paper.pdf}
  % \caption{RP overview. An application uses the Pilot API to describe pilots
  %   (green squares) and units (red circles). The PilotManager (purple box)
  %   instantiates (dash arrow) pilots, the UnitManager (purple box)
  %   instantiates (solid arrow) units. Both managers are executed on the user
  %   workstation. Pilots are launched (dashed arrows) on resources A and B
  %   via SAGA API, an Agent (purple box) is bootstrapped for each pilot
  %   (green box), units (solid red circles) are scheduled to the Agents via
  %   MongoDB and executed by the Agent's Executer (yellow box).
  \caption{NGE Architecture as deployed on Titan. The PilotManager and the
  UnitManager reside on one of Titan's DTN while the Agent is executed on
  Titan's worker nodes. Boxes color coding: gray for entities external to NGE,
  white for APIs, purple for NGE's modules, green for pilots, yellow for
  module's components.\mtnote{Change the picture eliminating Resource B.}}
\label{fig:arch-overview}
\end{figure}

@@

NGE exposes an API for the application layer to describe workloads
(Fig.~\ref{fig:arch-overview}, green squares) and pilots
(Fig.~\ref{fig:arch-overview}, red circles), and to instantiate a PilotManager
and a UnitManager. The PilotManager submits (Fig.~\ref{fig:arch-overview}, dash
arrow) pilots to Titan's PBS batch system via SAGA API, as done by PanDA Broker
to submit MPI scripts. Once scheduled, the pilot's Agent is bootstrapped on
Titan's workers nodes, and  the UnitManager schedules
(Fig.~\ref{fig:arch-overview}, solid arrow) units to the Agent's Executer for
execution. The UnitManager and the Agent communicate via a database that is
instantiated on one of Titan's DTN so to be reachable by both modules. A similar
approach would be used to enable PanDA Broker to schedule pilots instead of MPI
scripts.

@@

Agents of NGE run on MOM nodes or worker nodes, using the \emph{Open Run-Time
Environment (ORTE)}. ORTE is a spin-off from the Open-MPI project and is a
critical component of the OpenMPI implementation. It was developed to support
distributed high-performance computing applications operating in a heterogeneous
environment. The system transparently provides support for interprocess
communication, resource discovery and allocation, and process launching across a
variety of platforms. ORTE provides a mechanism similar to the Pilot concept -
it allows the user to create a \emph{``dynamic virtual machine''} (DVM) that
spans multiple nodes. ORTE provides libraries to enable the submission,
monitoring and managing of tasks, avoiding filesystem bottlenecks and race
conditions with network sockets. As a consequence, it is able to minimize the
system overhead while submitting tasks.

>>>>

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{figures/rp_architecture_compact_atlaswms_paper.pdf}
  % \caption{RP overview. An application uses the Pilot API to describe pilots
  %   (green squares) and units (red circles). The PilotManager (purple box)
  %   instantiates (dash arrow) pilots, the UnitManager (purple box)
  %   instantiates (solid arrow) units. Both managers are executed on the user
  %   workstation. Pilots are launched (dashed arrows) on resources A and B
  %   via SAGA API, an Agent (purple box) is bootstrapped for each pilot
  %   (green box), units (solid red circles) are scheduled to the Agents via
  %   MongoDB and executed by the Agent's Executer (yellow box).
  \caption{NGE Architecture as deployed on Titan. The PilotManager and the
  UnitManager reside on one of Titan's DTN while the Agent is executed on
  Titan's worker nodes. Boxes color coding: gray for entities external to NGE,
  white for APIs, purple for NGE's modules, green for pilots, yellow for
  module's components.}
\label{fig:arch-overview}
\end{figure}

@@

NGE exposes an API for the application layer to describe workloads
(Fig.~\ref{fig:arch-overview}, green squares) and pilots
(Fig.~\ref{fig:arch-overview}, red circles), and to instantiate a PilotManager
and a UnitManager. The PilotManager submits pilots to Titan's PBS batch system
via SAGA API (Fig.~\ref{fig:arch-overview}, dash arrow), as done by PanDA Broker
to submit MPI scripts. Once scheduled, the pilot's Agent is bootstrapped on
Titan's MOM node and worker nodes, and  the UnitManager schedules units to the
Agent's Scheduler (Fig.~\ref{fig:arch-overview}, solid arrow). The Agent's
Scheduler schedules the units on one or more Agent's Executor for execution. The
Agent's executors can manage one or more worker nodes, depending on performance
evaluations.

The UnitManager and the Agent communicate via a database that is instantiated on
one of Titan's DTN so to be reachable by both modules. A similar approach would
be used to enable PanDA Broker to schedule pilots instead of MPI
scripts.\mtnote{Rewrite this after checking it with Andre.}

@@

The NGE Agent uses the \emph{Open Run-Time Environment (ORTE)} for communication
and coordination of units execution. ORTE is a spin-off from the Open-MPI
project and is a critical component of the OpenMPI implementation. It was
developed to support distributed high-performance computing applications
operating in a heterogeneous environment. The system transparently provides
support for interprocess communication, resource discovery and allocation, and
process launching across a variety of platforms. ORTE provides a mechanism
similar to the Pilot concept - it allows the user to create a \emph{``dynamic
virtual machine''} (DVM) that spans multiple nodes. ORTE provides libraries to
enable the submission, monitoring and managing of tasks, avoiding filesystem
bottlenecks and race conditions with network sockets. As a consequence, it is
able to minimize the system overhead while submitting tasks.
